Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-03 paper.tex
fix: 文段中表格号加粗

The validation success rates for models trained on the 15 decomposed actions are presented in Table~\ref{tab2}, with each model evaluated over 10 trials.

>>>>

The validation success rates for models trained on the 15 decomposed actions are presented in \textbf{Table~\ref{tab2}}, with each model evaluated over 10 trials.
